### 2019-06-11 Manuscript/Data_Repository/Data_Repository.tex
add template for data repository

%\usepackage{fontspec}
%\usepackage[utf8]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{amsmath,amssymb}
\usepackage[normalem]{ulem}
\usepackage[left]{lineno}
\usepackage{booktabs}
\usepackage{changepage}
\usepackage{rotating}
\usepackage{color}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage[hidelinks]{hyperref}
\urlstyle{same}
\usepackage{threeparttable}
\doublespacing

\raggedright
\textwidth = 6.5 in
\textheight = 8.25 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.5 in
\parskip = 0.1 in
\parindent = 0.2in

@@

% Self defined commands
\newcommand{\degC}{$^{\circ}$C\xspace}
\newcommand{\dC}{$\delta^{13}$C\xspace}
\newcommand{\dO}{$\delta^{18}$O\xspace}
\newcommand{\SrSr}{$^{87}$Sr/$^{86}$Sr\xspace}
\newcommand{\permil}{\textperthousand\xspace}
\newcommand{\dsil}{$d$\xspace}
\newcommand{\UPb}{$^{206}$Pb/$^{238}$U\xspace}
%

\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{Park et al., in preparation for XXX}
\rhead{\thepage}

@@

\begin{flushleft}
{\Large \textbf{GEOCLIM Modern}}

Yuem Park\textsuperscript{1},
Nicholas L. Swanson-Hysell\textsuperscript{1}

\bigskip
\textsuperscript{1} Department of Earth and Planetary Science, University of California, Berkeley, CA, USA

\textsuperscript{2} XXX
\bigskip

@@

\noindent\textit{This article is in preparation for XXX}

@@

\section*{ABSTRACT \label{sec:ABSTRACT}}

@@

\section*{INTRODUCTION \label{sec:INTRODUCTION}}

\section*{METHODS}

\section*{RESULTS}

\section*{DISCUSSION}

\section*{ACKNOWLEDGEMENTS \label{sec:ACKNOWLEDGEMENTS}}

\clearpage
\newpage

\section*{TABLES}

\clearpage
\newpage

\section*{FIGURES}

\clearpage
\newpage
\footnotesize

@@

>>>>

%\usepackage{fontspec}
%\usepackage[utf8]{inputenc}
\usepackage{textcomp,marvosym}
\usepackage{amsmath,amssymb}
\usepackage[normalem]{ulem}
\usepackage[left]{lineno}
\usepackage{changepage}
\usepackage{rotating}
\usepackage{color}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{threeparttable}
\usepackage{color,colortbl}
\usepackage{url}
%\usepackage[hidelinks]{hyperref}
\urlstyle{same}
\doublespacing

\raggedright
\textwidth = 6.5 in
\textheight = 8.25 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.5 in
\parskip = 0.1 in
\parindent = 0.1in

@@

% Self defined commands
\newcommand{\degC}{$^{\circ}$C\xspace}
\newcommand{\dC}{$\delta^{13}$C\xspace}
\newcommand{\dO}{$\delta^{18}$O\xspace}
\newcommand{\SrSr}{$^{87}$Sr/$^{86}$Sr\xspace}
\newcommand{\permil}{\textperthousand\xspace}
\newcommand{\dsil}{$d$\xspace}

\setcounter{figure}{0}
\renewcommand{\thefigure}{DR\arabic{figure}}
\setcounter{table}{0}
\renewcommand{\thetable}{DR\arabic{table}}

\definecolor{Yellow}{rgb}{1,1,0.35}
%

\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{Park et al., in review for XXX}
\rhead{\thepage}

@@

\begin{flushleft}
{\Large \textbf{Data Repository for ``GEOCLIM Modern''}}
\\
Yuem Park\textsuperscript{1},
\\
\bigskip
\textsuperscript{1} Department of Earth and Planetary Science, University of California, Berkeley, CA, USA
\\
\bigskip

@@

@@

This document accompanies the discussion contained in the main text. All the Python code used for this study, as well as the associated data tables not included in this document, can be found at: \url{https://github.com/Swanson-Hysell-Group/XXX}.

\clearpage

\section*{XXX}

@@

\clearpage

@@

\newpage
